Guided Proofreading of Automatic Segmentations for Connectomics

### 2017-03-17 paper/results.tex
Some changes to 5.1.

\paragraph{L.~Cylinder.} Evaluation was performed on previously unseen sections of the mouse cortex volume from Kasthuri~\etal~\cite{kasthuri2015saturated}. We generated an unbalanced dataset of 81,184 correct and 8,780 split error patches with respect to the ground truth labeling. Then, we ranked each patch by using focused proofreading and guided proofreading, and compare classification performance (Fig. \ref{fig:pr}). Our method exhibits higher sensitivity.% for correct and erroneous patches.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{gfx/roc.pdf}
\caption{Receiver Operating Characteristic curves comparing focused proofreading and guided proofreading automatic correction. We evaluate on unbalanced tests sets of the AC4 subvolume (darker colors) and the L. Cylinder volume (lighter colors). Guided proofreading performs better.}
\label{fig:pr}
\end{figure}

>>>>

\paragraph{L.~Cylinder.} Evaluation was performed on previously unseen sections of the mouse cortex volume from Kasthuri~\etal~\cite{kasthuri2015saturated}. We generated a dataset of 81,184 correct and 8,780 split error patches with respect to the ground truth labeling. Then, we classified each patch by using focused proofreading and guided proofreading, and compare performance (Fig. \ref{fig:pr}). Our method exhibits higher sensitivity and lower fall-out.% for correct and erroneous patches.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{gfx/roc.pdf}
\caption{Receiver Operating Characteristic curves comparing focused proofreading and guided proofreading automatic correction. We evaluate on unbalanced test sets of the AC4 subvolume (darker colors) and the L. Cylinder volume (lighter colors). Guided proofreading performs better.}
\label{fig:pr}
\end{figure}
